Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-03-06 ProbabilisticCoherence.tex
Started on section 4

@@

Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}. However, this idea has not been explored in the context of probabilistic forecasting. Consequently, we Thus our main focus is to rigorously define the probabilistic forecast reconciliation and discuss how that definition can be used in practice.

@@

Initially we define point forecast reconciliation as a groundwork to the probabilistic forecast reconciliation.

\begin{definition}\label{def:reconpoint}
	Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $ and $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$. Then $\tilde{\bm{b}}_{t+h}$ is said to be reconciled bottom level forecasts if 
	\begin{equation}
	\tilde{\bm{b}}_{t+h}=\bm{g}(\hat{\bm{y}}_{t+h}),
	\end{equation}
	where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\mathbb{R}^m$. The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto the $\mathbb{C}^m$.
\end{definition}

Importance of definition (\ref{def:reconpoint}) is that it facilitates for both linear and non-linear reconciliation. In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear. On the other hand, if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(.)$ will linearly projects incoherent point forecasts onto $\mathbb{C}^m$. Latter was the main focus in previous studies in hierarchical point forecasting, where $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.

>>>>

Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the traditional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}. However, this idea has not been explored in the context of probabilistic forecasting.

@@

Initially we define point forecast reconciliation, before extending the idea to the probabilistic setting.

@@

\begin{definition}\label{def:reconpoint}
  Let $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$, and let 
  \begin{equation}
    \tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h}),
  \end{equation} 
  where $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m$. Then $\tilde{\bm{y}}_{t+h}$ is said to be ``reconciled'' if  $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto $\mathbb{C}^m$.
\end{definition}

The importance of Definition \ref{def:reconpoint} is that it allows for both linear and non-linear reconciliation. In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear. On the other hand, if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(.)$ will linearly projects incoherent point forecasts onto $\mathbb{C}^m$. Latter was the main focus in previous studies in hierarchical point forecasting, where $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
